Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
commit

@@

## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup

>>>>

# Load necessary libraries
library(tidyverse)
library(lubridate)

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
                          'Symptoms of Anxiety Disorder', 
                          'Symptoms of Anxiety Disorder or Depressive Disorder'))

# Ensure that 'Time.Period.End.Date' is a Date object
filtered_data$Time.Period.End.Date <- as.Date(filtered_data$Time.Period.End.Date, format = "%Y-%m-%d")

# Define the specific dates for the x-axis scale
specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
                            "2021-05-10", "2021-09-13", "2022-01-10", 
                            "2022-05-09", "2022-09-13", "2023-01-16",
                            "2023-05-08", "2023-09-04", "2024-01-08"))

# Plotting the line graph
ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

Both Anxiety and Depressive Disorder showing the similar trends over the period. 
## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-ageandtrend-graph
#| fig-cap: "Depressive Disorder Trend by Population Age Subgroup in US"

# Load necessary libraries
library(tidyverse)
library(lubridate)

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator == "Symptoms of Depressive Disorder")  # Assuming you need only this indicator

# Ensure that 'Time Period End Date' is a Date object
# Make sure to use the exact column name as it appears in your CSV file, including using backticks if necessary
filtered_data$`Time Period End Date` <- as.Date(filtered_data$`Time Period End Date`, format = "%Y-%m-%d")

# Define the specific dates for the x-axis scale
specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
                            "2021-05-10", "2021-09-13", "2022-01-10", 
                            "2022-05-09", "2022-09-13", "2023-01-16",
                            "2023-05-08", "2023-09-04", "2024-01-08"))

# Plotting the line graph
ggplot(filtered_data, aes(x = `Time Period End Date`, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
